### 2013-12-04 Publications/2013-ISBI14/04-results.tex
Last draft.

\begin{figure*}[tpb]
   \centering
   \includegraphics[width=0.80\textwidth]{Fig02-Results}
   \caption{Visual evaluation of the correction methods.
   First row represents a coronal section of the \textit{b0} volume. 
   In second row, the outcome of tractography after filtering tracks
   that did not connect two regions.
   Third row shows the associated connectivity matrices. All the matrices
   are compared to the ground-truth connections in the phantom. The existing
   connections that were correctly detected at each step are depicted in white
   color. False positives have been marked in red and false negatives in blue.
   Gray color represents the true negatives (non-existent connections correctly detected).}
   \label{fig:results}
\end{figure*}

>>>>

\begin{figure*}[tpb]
   \centering
   \includegraphics[width=0.8\linewidth]{Fig02-Results}
   \caption{Visual assessment of the correction methods.}
   \label{fig:results}
\end{figure*}
